---
title: "Batch Size Optimization"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: simplex
    logo: smalllogo.png
---
<style type="text/css">

.side { 
   font-size: 20px;
   font-family: Frutiger;
}

</style>

```{r  include=FALSE}
library(data.table)
library(dplyr)
library(highcharter)
library(flexdashboard)
library("quantmod")
library(shiny)
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
source("KPI_Calculation.R")

```


KPIs By Cycle Stock {data-navmenu="Detail Dashboard" .storyboard}
=======================================================================

Sidebar {.sidebar data-width=auto class="side"}
-----------------------------------------------------------------------

Select Cycle Stock :


```{r}

checkboxGroupInput("check","",choices = cycleStock.List,selected = cycleStock.List[1])

```


-----------------------------------------------------------------------
### Daily Inventory Quantity

```{r echo=FALSE}

renderHighchart(
{
  m <- c("Cycle Stock","Day", "Inventory Quantity (unit)")
  n <- sprintf("{point.%s}", c("CycleStock","Day", "InventoryQuantity"))
  tltip <- tooltip_table(m, n)
  df.Inv$InventoryQuantity <- df.Inv$Inventory.Quantity
  Inv.cycle <- data.frame()
  for(i in 1 : length(input$check)){
    Inv <- subset(df.Inv,df.Inv$CycleStock == input$check[i])
    Inv.cycle <- rbind(Inv.cycle,Inv)
  }
  
  hc <- hchart(Inv.cycle, "line", hcaes(x = Day, y = Inventory.Quantity, group = CycleStock)) %>%
    hc_xAxis(title = list(text = "Day")) %>%
    hc_yAxis(title = list(text = "Inventory Quantity(unit)")) %>%
    hc_title(text = "Daily Inventory") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
hc
})
```

### Daily Sales Quantity

```{r echo=FALSE}

renderHighchart(
{
  m <- c("Cycle Stock","Day", "Sales Quantity (unit)")
  n <- sprintf("{point.%s}", c("CycleStock","Day", "SalesQuantity"))
  tltip <- tooltip_table(m, n)
  Sales.cycle <- data.frame()
  for(i in 1 : length(input$check)){
    Sale <- subset(df.Sales,df.Sales$CycleStock == input$check[i])
    Sales.cycle <- rbind(Sales.cycle,Sale)
  }
  
  hc <- hchart(Sales.cycle, "line", hcaes(x = Day, y = SalesQuantity, group = CycleStock)) %>%
    hc_xAxis(title = list(text = "Day")) %>%
    hc_yAxis(title = list(text = "Sales Quantity(unit)")) %>%
    hc_title(text = "Daily Sales") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
hc
})
```

### Daily Produced Quantity

```{r echo=FALSE}

renderHighchart(
{
  m <- c("Cycle Stock","Day", "Produced Quantity (unit)")
  n <- sprintf("{point.%s}", c("CycleStock","Day", "ProdQuantity"))
  tltip <- tooltip_table(m, n)
  Prod.cycle <- data.frame()
  for(i in 1 : length(input$check)){
    prod <- subset(df.Prod,df.Prod$CycleStock == input$check[i])
    Prod.cycle <- rbind(Prod.cycle,prod)
  }
  
  hc <- hchart(Prod.cycle, "line", hcaes(x = Day, y = ProdQuantity, group = CycleStock)) %>%
    hc_xAxis(title = list(text = "Day")) %>%
    hc_yAxis(title = list(text = "Produced Quantity(unit)")) %>%
    hc_title(text = "Daily Produced") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
hc
})
```

KPIs by SKU {data-navmenu="Detail Dashboard" .storyboard}
=======================================================================

Sidebar {.sidebar data-width=auto class="side"}
-----------------------------------------------------------------------
Write something here


```{r}

selectInput("x", "Select SKU:", choices = list.SKUs)
                  
```


-----------------------------------------------------------------------

### Sales by SKU

```{r}
renderHighchart(
  {
  sales1SKU <- subset(df.Sales.SKU,df.Sales.SKU$SKU == input$x)
  sales1SKU <- sales1SKU[order(sales1SKU$CycleStock,decreasing = FALSE),]
  
  m <- c("Cycle Stock", "Sales (unit)")
  n <- sprintf("{point.%s}", c("CycleStock", "Sales"))
  tltip <- tooltip_table(m, n)

  hc <- hchart(object = sales1SKU, "line", hcaes(x = CycleStock, y = Sales)) %>%
    hc_xAxis(title = list(text = "Cycle Stock")) %>%
    hc_yAxis(title = list(text = "Sales (unit)")) %>%
    hc_title(text = "Sales unit by cycle stock") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
  
  hc
  # print(ggplot(data = sales.oneSKU, aes(x = Day, y = ActualSales)) + geom_line())
  })
```

### Average Inventory by SKU

```{r}
renderHighchart(
  {
  inv1SKU <- subset(df.Inv.SKU,df.Inv.SKU$SKU == input$x)
  inv1SKU <- inv1SKU[order(inv1SKU$CycleStock,decreasing = FALSE),]
  
  m <- c("Cycle Stock", "Average Inventory (unit)")
  n <- sprintf("{point.%s}", c("CycleStock", "AvgInventory"))
  tltip <- tooltip_table(m, n)

  hc <- hchart(object = inv1SKU, "line", hcaes(x = CycleStock, y = AvgInventory)) %>%
    hc_xAxis(title = list(text = "Cycle Stock")) %>%
    hc_yAxis(title = list(text = "Average Inventory (unit)")) %>%
    hc_title(text = "Average inventory by cycle stock") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
  
  hc
  # print(ggplot(data = sales.oneSKU, aes(x = Day, y = ActualSales)) + geom_line())
  })
```

### Produced Quantity by SKU

```{r}
renderHighchart(
  {
  prod1SKU <- subset(df.Prod.SKU,df.Prod.SKU$SKU == input$x)
  prod1SKU <- prod1SKU[order(prod1SKU$CycleStock,decreasing = FALSE),]
  
  m <- c("Cycle Stock", "Produced Quantity (unit)")
  n <- sprintf("{point.%s}", c("CycleStock", "ProducedQty"))
  tltip <- tooltip_table(m, n)

  hc <- hchart(object = prod1SKU, "line", hcaes(x = CycleStock, y = ProducedQty)) %>%
    hc_xAxis(title = list(text = "Cycle Stock")) %>%
    hc_yAxis(title = list(text = "Produced Quantity (unit)")) %>%
    hc_title(text = "Produced Quantity by cycle stock") %>%
    hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)
  
  hc
  # print(ggplot(data = sales.oneSKU, aes(x = Day, y = ActualSales)) + geom_line())
  })

```